Compositional equivalences based on Open pNets

### 2020-09-11 2016-Weak-FH-Bisim/Coverletter.tex
coverletter et .pdf

Considering the length of the submitted material,
 we   suggest to
keep the two first appendices in the final version of the paper (leading to a
paper of 73 pages) \Eric{if we keep A and B, we get 66 pages} because they are important to understand the paper.
The other appendices \Eric{there is only one left out in that case. So siingular. Did we change the structure of appendices ? Do you really intend to keep both A and B ?} will be available as a research report, we keep
them in the submission to ease the work of the reviewers. 
Of course, depending on the opinion of the reviewers, we could also move more material to  the body of the paper, or remove more proofs from the published version and only keep them in the report.

@@

Finally, after a brief exchange with Alexandra Silva, we improved the form of the paper as follows. We improved the spacings here and there (e.g. between subscripts and rest of text) and tracked overfull boxes. We also adopted a reduced number of symbols and tried to reduce the use of $<....>$ to the synchronisation vectors where this notation is usual now.

>>>>

Considering the length of the submitted material,
 we   suggest to
keep the two first appendices in the final version of the paper (leading to a
paper of 66 pages)  because they are important to understand the paper and contain the proofs.
The other appendix  will be available as a research report, we keep
them in the submission to ease the work of the reviewers. 
Of course, depending on the opinion of the reviewers, we could also move more material to  the body of the paper, or remove more proofs from the published version and only keep them in the report for example.

@@

Finally, after a brief exchange with Alexandra Silva, we improved the form of the paper as follows. We improved the spacings at some places (e.g. between superscripts and rest of text) and tracked overfull boxes. We also adopted a reduced number of symbols and tried to reduce the use of $<....>$ to the synchronisation vectors where this notation is usual now.
